### 2019-10-30 submission/manuscript.Rmd
Begin responding to reviewers

---
bibliography: references.bib
csl: mbio.csl
fontsize: 11pt
geometry: margin=1.0in
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
---

>>>>

---
bibliography: references.bib
csl: msphere.csl
fontsize: 11pt
geometry: margin=1.0in
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
---
